New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-07-31 paper/answer_rev_2.tex
wip

\documentclass[letterpaper]{letter}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{group-separator = {,}}

\usepackage{multirow}

%\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
%\newdefinition{rmk}{Remark}
%\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}
\usepackage[dvipsnames]{xcolor}

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}
\signature{Danilo Tedeschi}

\begin{document}

@@

		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint. That is, there is a non-overlapping solution, however, none of them is in the set of solutions we look for.

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}
		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

\end{document}

>>>>

@@

		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint. That is, there are non-overlapping solutions, however, it is possible to see that our algorithm would fail to find any -- try it yourself, notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}
